---
title: "Basic Usage on PBMC3k Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic-usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
suppressPackageStartupMessages({
library(Seurat)
library(callback)
})
```

```{r install_SeuratData}
devtools::install_github('satijalab/seurat-data')
library(SeuratData)
```

First, we use the `SeuratData` data package to first download and then load
2700 PBMCs. The loaded `SeuratObject`, `pbmc3k`, is from an old version of 
`Seurat`, and so we update the object to v5.

```{r load_data}
set.seed(123)

SeuratData::InstallData("pbmc3k")
data("pbmc3k")

pbmc3k <- UpdateSeuratObject(pbmc3k)
```

Now, we use `Seurat` to perform the usual preprocessing steps that are performed prior to clustering.

```{r preprocessing}
pbmc3k <- NormalizeData(pbmc3k)
pbmc3k <- FindVariableFeatures(pbmc3k)
pbmc3k <- ScaleData(pbmc3k)
pbmc3k <- RunPCA(pbmc3k)
pbmc3k <- FindNeighbors(pbmc3k)
pbmc3k <- RunUMAP(pbmc3k, dims = 1:10)
```

The `callback` algorithm can be run with a single function call as a drop-in
replacement for the `Seurat` function `FindClusters`.

```{r run_callback}
pbmc3k <- FindClustersCallback(pbmc3k)
```

The `callback`  clusters are set to the idents of the `SeuratObject` that is
returned by `FindClustersCallback`

```{r plot_umap}
DimPlot(pbmc3k)
```

Cluster labels from `FindClustersCallback` care stored in the metadata in the
column `pbmc3k@meta.data$callback_clusters`.

```{r plot_umap2}
DimPlot(pbmc3k, group.by = "callback_clusters")
```
